Psyc 601 Multivariate Statistics Project

### 2013-08-28 writeups/proposal/proposal.tex
foo
Former-commit-id: 1fa0c7bc892c2fe90369cfab2a4624f620989511 [formerly a05c9c05efd573c31e26cd5cb55a88144019fd06]
Former-commit-id: 6d9af6b8a25a27c7bc825a5ffa3804b5a381a9a6

The current state of research on Twitter hashtag prediction is that a mix of co-occurrence and latent-based models have been used to predict hashtags, and the results are encouraging.
However, there has been very little research on how a specific user's past hashtag use should influence the model's prediction when that user is composing a tweet.
\textcite{Kywe2012} did take a user-centered view with their model, but the hashtags predicted by the user and content were analyzed separately and then the top from each group were combined for prediction.
The ACT-R declarative memory retrieval model takes a combined approach, and shows how past user behavior and current context combine to produce the most likely retrieval.
Each component is summed together to generate a total activation, and then the likelihodd of chunks are ranked by that summed activation.
This technique allows for a more natural combination of the two components, where weights can be assigned to each component depending on how strongly each term predicts performance.
This type of weighted additive model that combines past user behavior and current tweet context to predict the most likely hashtags has not yet been explored for Twitter.

@@

>>>>

@@

There has been a mix of co-occurrence and latent-based models created to predict hashtags use on Twitter, and the results are encouraging.
However, there has been very little research on how a specific user's past hashtag use should influence the model's prediction when that user is composing a tweet.
\textcite{Kywe2012} did take a user-centered view with their model, but the hashtags predicted by the user and content were analyzed separately and then the top from each group were combined for prediction.
The ACT-R declarative memory retrieval theory shows how past user behavior and current context combine to produce the most likely retrieval.
Each component is summed together to generate a total activation, and then the likelihodd of chunks are ranked by that summed activation.
This technique allows for a more natural combination of the two components, where weights can be assigned to each component depending on how strongly each term predicts performance.
This type of weighted additive model that combines past user behavior and current tweet context to predict the most likely hashtags has not yet been explored for Twitter.
